---
title: "Network making"
author: "yt"
date: "2024/8/30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Network making

```{r load packages}
library(tidyr)
library(dplyr)
library(magrittr)
library(SummarizedExperiment)
library(NetCoMi)
load(file = 'tse.R'
```

It is also good to know the co-occurrence pattern in microbial communities. One potential way is network. Here I use netcomi package published <https://doi.org/10.1093/bib/bbaa290>

I noticed that there is also tutorial with mia team.

<https://microbiome.github.io/OMA/docs/devel/>

Here, SparCC network is built, the detailed methodology was used according to the report. These parameters were set similar to paper of

<https://microbiome.github.io/OMA/docs/devel/>

but at a simpler version as my computer gonna broken

```{r}

#double network

pseq <- makePhyloseqFromTreeSummarizedExperiment(tse)
pseq_genus <- phyloseq::tax_glom(pseq, taxrank = "Genus")

#separate the data
pseq_msi <- phyloseq::subset_samples(pseq_genus,MSI.Status == "MSI")
pseq_mss <- phyloseq::subset_samples(pseq_genus,MSI.Status == "MSS")

#construct networks 
net_sparcc_msi <- netConstruct(data = pseq_msi,
                               data2 = pseq_mss,
                           measure = "sparcc",
               #in the source code of sparcc,it alread normlize with clr
                           measurePar = list(iter = 50,
                                             inner_iter = 10,
                                             th = 0.3,
                                            nboot=100 # at least
                           ),
                           filtTax = "highestVar",
                           filtTaxPar = list(highestVar = 50),
                           #this variance is variance of p value
                           filtSamp = 'totalReads',
                           filtSampPar = list(totalReads=1000),
                           sparsMethod = 'bootstrap',#pseudo p values
                           adjust = 'lfdr',#adjust p value produced
                           lfdrThresh = 0.05,
                           verbose = 3,
                          seed = 123456)

#Hear is Pearson network, another option you could do, 
net_person <- netConstruct(data=pseq_msi,
                           data2=pseq_mss,
                          filtTax = "highestFreq",
                          filtTaxPar = list(highestFreq = 50),
                          measure = "pearson",
                          zeroMethod = "pseudo", 
                          normMethod = "clr",
                          sparsMethod = "threshold",
                          filtSamp = 'highestFreq',
                          filtSampPar = list(highestFreq=n_msi),
                          thresh = 0.4,
                          adjust = 'lfdr',
                          lfdrThresh = 0.05,
                          seed = 123456)
```

Next is to calculate some parameters of the network

```{r}


props_sparcc <- netAnalyze(net_sparcc_msi, 
                           clustMethod = "cluster_fast_greedy",
                           hubPar = c('eigenvector'),
                           normDeg = FALSE)
#making labels on graph
labels <- sapply(as.vector(pseq_genus@tax_table[, "Genus"]), function(x) gsub('g__','',x))
names(labels) <- rownames(pseq_genus@tax_table)
phyla <- as.factor(sapply(as.vector(pseq_genus@tax_table[, "Phylum"]), function(x) gsub('p__','',x)))
names(phyla) <-  rownames(pseq_genus@tax_table)

# Create color vector
Palette2 <- c('#8b8378','#458b74','#f0ffff','#eeb422','#ee6aa7','#8b3a62','#cd5c5c','#ee6363','#f0e68c','#e6e6fa','#add8e6','#bfefff','#f08080','#d1eeee','#7a8b8b','#8b814c','#8b5f65','gray','blue', 'orange', 'green', 'yellow', 'red', 'hotpink', 'cyan','purple', 'burlywood1','skyblue','grey')


#plot it!
plot(props_sparcc, 
     sameLayout=TRUE,
     layoutGroup='union',
     rmSingle='inboth',
     labels=labels,
     repulsion=0.9,
     nodeColor = "feature",
     featVecCol = phyla, 
     colorVec =  Palette2,
     nodeTransp = 20,
     sameColThresh = 2,
     edgeFilter='threshold',
     edgeFilterPar=0.2,
     nodeSize = "clr",
     labelScale = F,
     labelFont = 2,
     cexNodes = 2, 
     cexLabels = 1,
     cexHubLabels = 1,
     cexTitle = 1,  
     shortenLabels='intelligent',
     edgeTranspHigh = 20,
     title1 = 'MSI',
     title2 = 'MSS',
     showTitle = TRUE,
     hubBorderCol  = "darkgray",
     mar=c(1,4,4,4))

#check some result 
summary(props_sparcc, groupNames = c("MSI", "MSS"))

#compare networks
comp_sparcc<- netCompare(props_sparcc, 
                          permTest = TRUE,
                          verbose = FALSE,
                          seed = 123456)


#find significant differences between plots
diff_pearson <- diffnet(props_sparcc,
                       diffMethod = "fisherTest", 
                       adjust = 'BH')

```

I didn't really ran it on my computer, because it is fragile and I ran it for too many times.

You could see the result in the report
